Ultra Diffuse Galaxies associated with Milky-Way Analogs

### 2022-08-31 main.tex
very first intro and abstract

%% Mark off the abstract in the ``abstract'' environment. 
\begin{abstract}

\end{abstract}

@@

\jiaxuan{Just copied the intro from the Magellan proposal. Not in shape at all.}
Since the discovery of ultra-diffuse galaxies (UDGs, defined to have $r_e > 1.5$ kpc and $\mu(g,0)>24.0\ \mathrm{mag\ arcsec^{-2}}$) in the Coma cluster \citep{vanDokkum2015}, there have been a variety of studies for these extreme systems ranging from their dark matter content \citep{vanDokkum2018,vanDokkum2019} to their globular cluster populations (Danieli et al. 2022). A central question related to UDGs is what physical mechanisms are responsible for their formation. Before we can answer this question, it is important to reliably determine in what environment they live.

Past UDG studies focused on rich galaxy groups and clusters \citep[e.g.,][]{Yagi2016,Zaritsky2019}, which provides distance information. Although UDGs are also found in field environments \citep{Prole2019,Tanoglidis2021,Kadowaki2021}, most studies of field UDGs lack distances and thus are statistical in nature. UDGs in groups and clusters are red and quenched; their blue counterparts are typically found in field environments (for some exceptions see \citealt{Roman2019,Prole2019}). This suggests that environment plays a crucial role in the formation and quenching of UDGs. Tidal effects and ram-pressure stripping explains the high quenched fraction in clusters and groups, but it is unclear whether field UDGs quench because of internal processes (feedback) and/or external processes (as splashback satellites, \citealt{Benavides2021}). It is also unclear whether UDGs belong to a special class of galaxy or are just a natural extension of dwarf systems to the lower surface brightness end. A larger UDG sample, especially in low-density environments, is needed to test these hypotheses.

Distance information of LSBGs is hard to know \citep{Kadowaki2021,Greene2022,Zaritsky2022} (also another cross-correlation paper recently?). Thus we turn to match with MW analogs.

UDG quenching: most studies found red UDGs in clusters, blue UDGs in fields \citep{Prole2019,Leisman2017}, however there are one or two red UDGs in fields. It is unclear 1) are UDGs born to be large and diffuse (Amorisco); 2) if not, how are they puffed up? 3) how are they quenched? what's the correlation between quenching and puffing.

explain those acronyms (SAGA, ELVES)

The best knowledge we have about dwarf galaxies at the very faint end was derived from systems in the Local Volume \citep[e.g.,][]{Simon2019,CarlstenELVES2022}. To better compare UDGs with other dwarf systems, we turned to looking for UDGs in the vicinity of Milky Way analogs at $0.01 < z < 0.04$. Until now, there are only $\sim 30$ confirmed UDGs associated with MW analogs \citep{Cohen2018,SAGA-II,CarlstenELVES2022}. The occurrence rate of UDGs in these low-density environments is unknown, and whether UDGs are quenched in such a regime has not been explored. With a sample of UDGs around MW-like hosts, we can compare the structural parameters, quenched fractions, nucleation fractions, and radial distributions with normal satellites in the nearby universe \citep[e.g.,][]{SAGA-II,CarlstenELVES2022}, to shed light on questions about the formation and evolution of the UDGs.

Stellar population of UDGs \citep[e.g.,][]{Gu2018}

Also compare with LCDM-based hydro sims. Study the quenching along the direction perpendicular to the mass-size.

While satellite galaxies in the fields are star-forming \citet{Geha2012}.

The goal of this work is to posit UDGs in the framework of satellite systems of MW analogs. We compare the statistical properties of UDGs with LV satellites and simulations. Try to figure out whether UDG is a special class of galaxies or they are just a tail of mass-size scatter.

This paper is framed as follows. We detect LSBGs, then match them to MW analogs such that we can assume distances.

@@

MW satellites: \citep{Nashimoto2022}

We adopt a $\Lambda$CDM cosmology from \citet{Planck15} with $\Omega_{\rm m}= 0.307$ and $H_0 = 67.7\ $km s$^{-1}$ Mpc$^{-1}$. We use the AB system \citep{Oke1983} for magnitudes. The stellar mass used in this work is based on a \citet{Chabrier2003} initial mass function.

@@

\section{LSBG search in HSC PDR2}
Continuing the work in \citet{Greco2018} (hereafter \citetalias{Greco2018}), we conduct a systematic search for low surface brightness galaxies in the PDR2 data, which covers $\sim 1.5$ of the sky area in \citetalias{Greco2018}. The schematic of the searching method in this paper remains similar to that in \citetalias{Greco2018}, but we do improve the searching completeness and purity by adding several new steps, which are highlighted in this section. For those who do not want to be bothered by technical details, we outline the major steps below:
\begin{enumerate}
    \item Source Detection (Sec. \ref{sec:detection}): we run \code{Source Extractor} on the coadd images after removing bright extended sources. Then we apply an initial size and color cut based on the output catalog. 
    \item Deblending (Sec. \ref{sec:deblending}): we remove false positives that are not likely to be LSBGs by running \code{scarlet}. We use \code{scarlet} models to define color-size-morphology-surface brightness cuts. This step removes roughly 97\% of false positives.
    \item Modeling (Sec. \ref{sec:modeling}): we fit a parametric model to the LSBGs to estimate their structural parameters. 
    \item Completeness and measurement uncertainties (Sec. \ref{sec:comp_meas}) are characterized by injecting mock \sersic{} galaxies into images. 
\end{enumerate}

@@

\section{UDGs in Milky-Way analogs}

@@

The concept of UDG was proposed for those dwarf galaxies with large physical size and diffuse light distribution. However, the size of a galaxy is strongly correlated with its mass, known as the mass-size relation \citep[e.g.,][]{Lange2015}. The slope of the mass-size relation has been shown to be color-dependent for galaxies above $M_\star > 10^{8.5}\ M_\odot$: blue star-forming galaxies have a shallower slope, whereas red quenched galaxies have a steeper slope. However, recent works show that the mass-size relation in the dwarf galaxy regime ($10^{5.5} < M_\star < 10^{8.5}$) is quite universal: the slope and intercept are not sensitive to the color and morphology of dwarf galaxy \citep{ELVES-I}. This gives us a chance to define a subset of dwarf galaxies that are outliers on the mass-size plane. Taking the measured mass-size relation from \citet{ELVES-I} $\log\, (r_e/\mathrm{pc}) = 0.247\, \log\, (M_\star/M_\odot) + 1.071$ and a scatter of $\sigma=0.181$ dex, we define a population of ultra-puffy galaxies (UPGs) to be galaxies that are $>1.5\sigma$ above the mass-size relation. The UPGs are not necessarily large in physical size or faint in average surface brightness, but they are outliers in size for their masses. Both UDG and UPG represent subsets of dwarf galaxies that are larger and more diffuse than average. However, the hard cut on size (1.5 kpc) means that the UDG definition excludes ``large'' galaxies at the low-mass end because as mass goes smaller, the average size also gets smaller. The surface brightness cut also biases the UDG sample because of mass-to-light ratio differences between blue and red galaxies, as will be discussed in Section \ref{sec:quench}. The definition of UPG based on the observed mass-size relation is more physically-motivated, and UPGs better represent a homogeneous subset of dwarf galaxies along the stellar mass axis. There is also no color preference in the UPG definition for a given stellar mass. It is worth noting that a definition based on the mass-size relation was already used in simulation studies where simulations cannot reproduce the observed mass-size relation \citep[e.g.,][]{Benavides2021}.

@@

\begin{figure*}
	\vbox{ 
		\centering
		\includegraphics[width=1\linewidth]{udg_upg_sample.pdf}
	}
    \caption{The distribution of galaxies in the ultra-diffuse galaxy (UDG) sample (\textit{left}) and the ultra-puffy galaxy (UPG) sample (\textit{right}). The UDGs are galaxies with $r_e>1.5$ kpc and $\sbeff > 25.0\ \sbunit$. The UPGs is defined to be $1.5\sigma$ above the mass-size relation in \citet{ELVES-I}. We split the samples into two color bins and show them in red ($g-i>0.8$) and blue ($g-i<0.8$). The marginal histograms are not normalized to highlight the relative number of red and blue galaxies. Compared with the UDG sample, the UPG sample includes blue galaxies with surface brightness higher than the UDG cut ($\sbeff < 25\ \sbunit$) and excludes red galaxies at $25 < \sbeff < 26\ \sbunit$.
    }
    \label{fig:udg_upg_re_mu}
\end{figure*}

@@

In Figure \ref{fig:mass_size}, we show our UDGs and UPGs on the mass-size plane color-coded by $\Delta(\mathrm{Quench})$ indicating how much a galaxy has been quenched. As we described in Section \ref{sec:mass-size}, the UDG sample includes a number of galaxies below the $1.5\sigma$ mass-size line. Additionally, these galaxies are mostly quenched (having zero or negative $\Delta(\mathrm{Quench})$). In order to help understand this phenomenon, we plot constant surface brightness lines of $\sbeff=25.0\ \sbunit$ for two different colors $g-i=0.4$ (blue solid line) and $g-i=0.8$ (red solid line). For our redshift range, the cosmological dimming effect is negligible and the surface brightness is a constant with distance. For a given size, surface brightness (e.g., $\sbeff=25.0\ \sbunit$), redder galaxies have the same absolute magnitude as blue galaxies, but have larger stellar mass because they have larger mass-to-light ratio than blue galaxies. The mass-to-light ratio effect manifests itself on Figure \ref{fig:mass_size} by separating the two constant surface brightness lines apart. We recall that the UDG is defined to have $r_e > 1.5$ kpc and $\sbeff > 25.0\ \sbunit$. As a result of the color-M/L relation, the UDG sample includes more red galaxies than blue ones by having a surface brightness cut at $\sbeff=25.0\ \sbunit$, and thus give rise to a high quenched fraction as we see in Figure \ref{fig:qfrac}. It is the pathological definition of UDG that makes the quenched fraction high.

We note that the color-$M_\star/L$ relation are only invoked when converting the absolute magnitude to stellar mass. Thus when studying the quenched fraction as a function of absolute magnitudes, the dependence of

one will 't see a high and constant quenched fraction for UDGs.

We advocate that UPGs better represent the large-size tail of the dwarf galaxy population and have a more objective definition.

Dwarf galaxy: most of them are blue in field, and most satellites of MW and larger groups/clusters are quenched.

Find literature for quenched fraction as a function of distance to host (Einasto 1974, Spekkens2014, Karunakaran2022 for MW and M31).

% \citep{Baxter2021}: machine learning derived quenched fraction

% \citep{Akins2021}: quenched fraction and quenching timescale in DC Justice League simulation.

% \citep{Samuel2022}: quenched fraction of MW sats in FIRE-2.

When discussing the quenched fraction, also mention that we are uncertain about the mass-size above 8.5 and below 9-ish? because we don't know about their mass-size.

The mass-size doesn't depend on color (carlsten). The quenched fraction also doesn't depend on size. Reflect on Danieli\&vD mass-size slice paper.

SAGA misses a fraction of red faint galaxies in their initial detection catalogs. This also explains the low quenched fraction of SAGA \citep{CarlstenELVES2022}.
SAGA SB limit is 25. ARTEMIS is able to reproduce SAGA quenched fraction.

\jiaxuan{UPG help us define mass-size lognormal, more diverse environment. distances.}

\citet{Trujillo2020}: define size based on surface mass density

From \citet{Wright2021}, We can take this into our paper: At high mass (M⋆ > 108 M⊙), most galaxies have reff > 1.5 kpc. UDGs are therefore those galaxies that are unusually LSB. At low mass (M⋆ < 107.5 M⊙), most galaxies have μ0,g > 24 mag arcsec−2. UDGs are therefore those galaxies that have unusually large effective radii. It is only really at intermediate masses that both the central surface brightness and the effective radius criteria are relevant.

discuss pros and cons of UDG and UPG (you have to assume a distance to define UPG).

% \subsection{Systematic search for LSBGs in the LSST era}

\subsection{UDG and UPG formation}
In this paper, one surprising finding is that although UPGs have extremely large size for their stellar mass, they have similar quiescent fraction as normal satellites in MW analogs. In ELVES, Greene et al. (in prep) also find no trend of quenched fraction on size. \citet{ELVES-I} find that the mass-size relation of satellites in MW analogs does not depend on the morphology (equivalently color) of satellites, suggesting that the quenching and morphological transformation involves very mild size evolution. Perhaps quenching and size growth happen separately. Then the question is what physics is responsible for the two processes respectively. In this section, we first review the quenching of MW satellites and the mechanisms for puffing up normal dwarfs to produce UDGs (UPGs). Then we combine the results presented in Section \ref{sec:results} and discuss possible implications on the formation and quenching of UDGs and UPGs.

%%%%%%%%%%%%%%%%%%%
Isolated dwarf galaxies in the field are known to be star-forming \citep{Geha2012}, but satellites in the Local Group and Local Volume are more quiescent \citep{Grcevich2009,Spekkens2014,Wetzel2015,Putman2021,CarlstenELVES2022}. This difference hints that the MW environments play an important role in regulating the star formation activities in dwarf galaxies. There have been extensive works using simulations to study the quenching of satellites in MW analogs \citep[e.g.,][]{Simpson2018,Buck2019,Garrison-Kimmel2019,Simons2020,Joshi2021,Akins2021,Karunakaran2021,Font2022,Samuel2022}, and many of them are able to reproduce the observed quenched fraction in the Local Group and in the Local Volume.

@@

\section{Summary}
\begin{itemize}
    \item we advocate studies for the quenched fraction as a function of size in simulations

>>>>

%% Mark off the abstract in the ``abstract'' environment. 
\begin{abstract}
Ultra-diffuse galaxies (UDGs) are dwarf galaxies with extreme sizes and low surface brightness. The formation and quenching mechanisms of these intriguing objects are still under debate. In this work, we present systematic search for ultra-diffuse galaxies associated with Milky Way (MW) analogs in the nearby Universe ($0.01 < z < 0.04$) using the Hyper Suprime-Cam Strategic Survey Program data. We also define a new subset of low surface brightness galaxies dubbed as ``ultra-puffy galaxies'' (UPGs) which better characterize the size outliers on the mass-size plane. We perform statistical studies for UDGs and UPGs and compare the results with previous studies for UDGs in clusters and groups. We further contrast UDGs and UPGs with the bulk of MW satellites in nearby Universe and simulations. We find that UDGs have a higher quenched fraction than MW satellites and the quenched fraction remains constant over 1 dex in stellar mass. We argue that this high quiescent fraction is an artifact of the UDG definition. Despite their large sizes, UPGs have similar quenched fractions as the MW satellites. These results might hint that the size growth and quenching of UPGs must happen separately. 
\end{abstract}

@@

Ultra-diffuse galaxies (UDGs), defined as dwarf galaxies with large size ($r_e > 1.5$ kpc) and low surface brightness ($\mu(g,0)>24.0\ \mathrm{mag\ arcsec^{-2}}$), have attracted much attention to study their formation and properties. Although being identified in the past \citep[e.g.,][]{Sandage1984,Caldwell1987,Impey1988,McGaugh1995,Dalcanton1997a}, UDGs come to the stage again after \citet{vanDokkum2015} discovered a large population of ultra-diffuse galaxies in the Coma cluster, accompanied by many other works on detecting UDGs in clusters \citep[e.g.,][]{Koda2015,Mihos2015,Yagi2016,vdBurg2016,vdBurg2017,Lee2017,Zaritsky2019}, groups \citep[e.g.,][]{Roman2017b,Greco2018,SAGA-II,CarlstenELVES2022}, and fields \citep[e.g.,][]{Leisman2017,Roman2019,Prole2019,Tanoglidis2021,Kadowaki2021}. There have been a variety of studies for these extremely-diffuse galaxy systems ranging from their dark matter content \citep[e.g.,][]{Mowla2017,vanDokkum2018,vanDokkum2019,Wasserman2019,Keim2022}, globular cluster populations \citep[e.g.,][]{vanDokkum2017,Somalwar2020,Forbes2020,Danieli2022}, and stellar populations \citep[e.g.,][]{Gu2018,Ferre-Mateu2018,Villaume2022}.

A central question for the UDG population is what physical mechanisms are responsible for their formation and quenching. Different mechanisms are proposed to explain the presence of UDGs in different environments. Field UDGs might formed after star-formation feedback \citep{DiCintio2017,Chan2018}, early galaxy mergers \citep{Wright2021}, being backsplash satellites \citep{Benavides2021}, or they were born in halos with higher spin \citep{Dalcanton1997,Amorisco2016,Liao2019}. For UDGs in groups and clusters, they are believed to be puffed up by tidal heating near the pericenter \citep{Jiang2019} or undergo adiabatic expansion due to mass loss \citep{Tremmel2020}. Despite advances in theoretical works, it is still an open question that how UDGs in certain environments are formed and quenched. It is also unclear whether UDGs belong to a special class of galaxy or are just a natural extension of dwarf systems to the lower surface brightness end. To answer these questions, a complete sample of ``normal'' satellites is needed to be compared with UDGs in the same environments.

Our best knowledge in the dwarf galaxy regime is about the satellite system of our Milky Way (MW) and the Local Group (LG) \citep[e.g.,][]{McConnachie2012,Simon2019}. With the advent of deep sky surveys and dedicated spectroscopy programs, the satellite systems of MW analogs in the Local Volume and nearby Universe become approachable. The Satellites Around
Galactic Analogs (SAGA) survey is designed to spectroscopically confirm the satellites of 100 MW analogs at $z\sim0.01$ \citep{SAGA-I,SAGA-II}. The Exploration of Local VolumE Satellites (ELVES) survey uses the deep imaging data to identify satellite candidates of MW-like hosts in the Local Volume ($D<12$ Mpc) and estimate the surface brightness fluctuation distances from images to confirm satellites \citep{ELVES-I,ELVES-II,CarlstenELVES2022}. Having the MW satellites as a reference frame, we can study UDG formation and quenching by comparing UDG with the bulk of observed and simulated MW satellites. However, there are only $\sim 30$ confirmed UDGs associated with MW analogs in literature \citep{Roman2017b,Cohen2018,SAGA-II,CarlstenELVES2022}. A larger sample of ultra-diffuse galaxies associated with MW hosts is needed to conduct such studies.

% One of the major obstacles for studying dwarf galaxies is that it is hard to get distance information especially for low-mass and low surface brightness galaxies. Beside direct distance measurements (e.g., SAGA, ELVES), it is common to assume a distance to a dwarf candidate by associating it with a host galaxy based on the projected angular distance \citep[e.g.,][]{vanDokkum2015,vdBurg2016,Wang2021,Zaritsky2022,Nashimoto2022}. A statistical background subtraction is needed to account for the contribution from background and foreground galaxies. Cross-correlation between the dwarf sample and a host galaxy sample can also reveal the distance distribution of dwarfs \citep{Greene2022}. These methods are also complemented by machine learning techniques \citep{Baxter2021,xSAGA-I}.

In this work, using the Hyper-Suprime Camera imaging data, we construct a UDG sample associated with MW analogs at $0.01 < z < 0.04$. The goal of this paper is to posit the low surface brightness galaxies in the framework of the satellite systems of MW analogs. We compare the statistical properties of UDGs with LV satellites and simulations to shed light on questions about the formation and evolution of the UDGs. We also propose a new definition for diffuse galaxies as ``ultra-puffy galaxies'' (UPGs) which better represent the large-size tail of the dwarf galaxy population.

% The occurrence rate of UDGs in these low-density environments is unknown, and whether UDGs are quenched in such a regime has not been explored. With a sample of UDGs around MW-like hosts, we can compare the structural parameters, quenched fractions, nucleation fractions, and radial distributions with normal satellites in the nearby universe \citep[e.g.,][]{SAGA-II,CarlstenELVES2022}, to shed light on questions about the formation and evolution of the UDGs.

% UDGs found in groups and clusters are mostly red and quenched, whereas their blue counterparts are found in field environments (although several quenched UDGs are found in the field, \citealt{Roman2019,Prole2019}). This suggests that environmental effects play a critical role in the formation and quenching of UDGs.

The layout of this paper is as follows. We describe the data we use in Section \ref{sec:data}. In Section \ref{sec:lsbg_search}, we describe how we search the LSBG candidates in HSC data, including source detection (\S \ref{sec:detection}), deblending (\S \ref{sec:deblending}), and modeling (\S \ref{sec:modeling}). We present our UDG and UPG samples in Section \ref{sec:sample_construction}. In Section \ref{sec:results}, we show statistical analysis for UDGs and UPGs including their abundances (\S \ref{sec:n_udg}), size distributions (\S \ref{sec:size_distr}), spatial distributions (\S \ref{sec:radial_distr}), and quenched fractions (\S \ref{sec:quench}). We discuss possible implications on the formation and quenching of LSB diffuse galaxies in Section \ref{sec:discussion}. Section \ref{sec:summary} presents a summary of this work and prospects for future works. We adopt a $\Lambda$CDM cosmology from \citet{Planck15} with $\Omega_{\rm m}= 0.307$ and $H_0 = 67.7\ $km s$^{-1}$ Mpc$^{-1}$. We use the AB system \citep{Oke1983} for magnitudes. The stellar mass used in this work is based on a \citet{Chabrier2003} initial mass function.

@@

@@

\section{LSBG search in HSC PDR2}\label{sec:lsbg_search}
Continuing the work in \citet{Greco2018} (hereafter \citetalias{Greco2018}), we conduct a systematic search for low surface brightness galaxies in the PDR2 data, which covers $\sim 1.5$ of the sky area in \citetalias{Greco2018}. The schematic of the searching method in this paper remains similar to that in \citetalias{Greco2018}, but we do improve the searching completeness and purity by adding several new steps, which are highlighted in this section. For those who do not want to be bothered by technical details, we outline the major steps below:
\begin{enumerate}
    \item Source Detection (Sec. \ref{sec:detection}): we run \code{Source Extractor} on the coadd images after removing bright extended sources. Then we apply an initial size and color cut based on the output catalog. 
    \item Deblending (Sec. \ref{sec:deblending}): we remove false positives that are not likely to be LSBGs by running \code{scarlet}. We use \code{scarlet} models to define color-size-morphology-surface brightness cuts. This step removes roughly 97\% of false positives.
    \item Modeling (Sec. \ref{sec:modeling}): we fit a parametric model to the LSBGs to estimate their structural parameters. 
    \item Completeness and measurement uncertainties (Sec. \ref{sec:comp_meas}) are characterized by injecting mock \sersic{} galaxies into images. 
\end{enumerate}

@@

\section{UDGs and UPGs in Milky-Way analogs}\label{sec:sample_construction}

@@

The concept of UDG was proposed for those dwarf galaxies with large physical size and diffuse light distribution. However, the size of a galaxy is strongly correlated with its mass, known as the mass-size relation \citep[e.g.,][]{Lange2015}. The slope of the mass-size relation has been shown to be color-dependent for galaxies above $M_\star > 10^{8.5}\ M_\odot$: blue star-forming galaxies have a shallower slope, whereas red quenched galaxies have a steeper slope. However, recent works show that the mass-size relation in the dwarf galaxy regime ($10^{5.5} < M_\star < 10^{8.5}$) is quite universal: the slope and intercept are not sensitive to the color and morphology of dwarf galaxy \citep{ELVES-I}. This gives us a chance to define a subset of dwarf galaxies that are outliers on the mass-size plane. Taking the measured mass-size relation from \citet{ELVES-I} $\log\, (r_e/\mathrm{pc}) = 0.247\, \log\, (M_\star/M_\odot) + 1.071$ and a scatter of $\sigma=0.181$ dex, we define a population of ultra-puffy galaxies (UPGs) to be galaxies that are $>1.5\sigma$ above the mass-size relation. The UPGs are not necessarily large in physical size or faint in average surface brightness, but they are outliers in size for their masses. Both UDG and UPG represent subsets of dwarf galaxies that are larger and more diffuse than average. However, the hard cut on size (1.5 kpc) means that the UDG definition excludes ``large'' galaxies at the low-mass end because as mass goes smaller, the average size also gets smaller. The surface brightness cut also biases the UDG sample because of mass-to-light ratio differences between blue and red galaxies, as will be discussed in Section \ref{sec:quench}. The definition of UPG based on the observed mass-size relation is more physically-motivated, and UPGs better represent a homogeneous subset of dwarf galaxies along the stellar mass axis. There is also no color preference in the UPG definition for a given stellar mass. It is worth noting that a definition based on the mass-size relation was already used in simulation studies where simulations cannot reproduce the observed mass-size relation \citep[e.g.,][]{Benavides2021}.
% \citet{Wright2021} can reproduce observed mass-size.

@@

\begin{figure*}
	\vbox{ 
		\centering
		\includegraphics[width=1\linewidth]{udg_upg_sample.pdf}
	}
    \caption{The distribution of galaxies in the ultra-diffuse galaxy (UDG) sample (\textit{left}) and the ultra-puffy galaxy (UPG) sample (\textit{right}). The UDGs are galaxies with $r_e>1.5$ kpc and $\sbeff > 25.0\ \sbunit$. The UPGs is defined to be $1.5\sigma$ above the mass-size relation in \citet{ELVES-I}. We split the samples into two color bins and show them in red ($g-i>0.8$) and blue ($g-i<0.8$). The marginal histograms are not normalized to highlight the relative number of red and blue galaxies. Compared with the UDG sample, the UPG sample includes blue galaxies with surface brightness higher than the UDG cut ($\sbeff < 25\ \sbunit$) and excludes red galaxies at $25 < \sbeff < 26\ \sbunit$. We note that this plot is not corrected for background contamination.
    }
    \label{fig:udg_upg_re_mu}
\end{figure*}

@@

In Figure \ref{fig:mass_size}, we show our UDGs and UPGs on the mass-size plane color-coded by $\Delta(\mathrm{Quench})$ indicating how much a galaxy has been quenched. As we described in Section \ref{sec:mass-size}, the UDG sample includes a number of galaxies below the $1.5\sigma$ mass-size line. Additionally, these galaxies are mostly quenched (having zero or negative $\Delta(\mathrm{Quench})$). In order to help understand this phenomenon, we plot constant surface brightness lines of $\sbeff=25.0\ \sbunit$ for two different colors $g-i=0.4$ (blue solid line) and $g-i=0.8$ (red solid line). For our redshift range, the cosmological dimming effect is negligible and the surface brightness is a constant with distance. For a given size, surface brightness (e.g., $\sbeff=25.0\ \sbunit$), redder galaxies have the same absolute magnitude as blue galaxies, but have larger stellar mass because they have larger mass-to-light ratio than blue galaxies. The mass-to-light ratio effect manifests itself on Figure \ref{fig:mass_size} by separating the two constant surface brightness lines apart. We recall that the UDG is defined to have $r_e > 1.5$ kpc and $\sbeff > 25.0\ \sbunit$. As a result of the color-M/L relation, the UDG sample includes more red galaxies than blue ones by having a surface brightness cut at $\sbeff=25.0\ \sbunit$, and thus give rise to a high quenched fraction as we see in Figure \ref{fig:qfrac}. It is the pathological definition of UDG that makes the quenched fraction high. We note that the color-$M_\star/L$ relation are only invoked when converting the absolute magnitude to stellar mass. Thus when studying the quenched fraction as a function of absolute magnitudes, the artifact on mass-size plane would disappears on the size-luminosity plane \citep[e.g., see][]{Danieli2019}.

In this paper, we propose an alternative definition for large diffuse galaxies: ultra-puffy galaxies (UPGs). They are defined to be $1.5\sigma$ above the average mass-size relation. The specific value above the average mass-size relation can be changed to probe different parts of the size distribution. As we discussed in Section \ref{sec:sample}, a mass-dependent size cut for diffuse galaxies is more objective than a hard size cut because the average size gets larger as increasing stellar mass. However, the mass-size relation generally depends on the color, morphology, environment, and also redshift of the galaxies \citep[e.g.,][]{Graham2003,Trujillo2007,vanDokkum2013,Cappellari2013,Lange2015}. Fortunately, for dwarf galaxies ($10^{5.5}\ M_\odot < M_\star < 10^{8.5}\ M_\odot$) in the nearby Universe, \citet{ELVES-I} find that the mass-size relation is not sensitive to the color and morphology. This finding encourages definitions based on the mass-size relation for diffuse galaxies. For the UPG population, we show that it has similar quenched fraction as the bulk satellite population of MW analogs (Fig. \ref{fig:qfrac}). From Fig. \ref{fig:mass_size}, it is clear that the UPG definition naturally represents the large-size tail of the mass-size relation without introducing the color-$M_\star/L$ artifacts on stellar mass. We thus advocate studying the UPG population and how the properties vary as a function of the puffiness (e.g., comparing UPG with $1.5\sigma$ with UPG with $2\sigma$).

However, everything comes with a price. In order to construct a UPG sample, one need to know the distance information as well as the color to convert observed magnitudes to stellar mass. The color-$M_\star/L$ relation also introduces additional uncertainties. \citet{ELVES-I} derive the mass-size relation below $M_\star \sim 10^{8.5}\ M_\odot$, whereas \citet{Lange2015} have relatively good constraints on the mass-size relation only above $M_\star \sim 10^{9}\ M_\odot$. As a result, it is not clear about the mass-size relation at $10^{8.5}\ M_\odot < M_\star < 10^{9}\ M_\odot$ and how it depends on color and morphology. In this work, we simply extrapolate \citet{ELVES-I} mass-size relation to $10^9\ M_\odot$. But the caveat on mass-size relation could make the UPG definition subject to systematical uncertainties. In this work we use the effective radius $r_e$, but other definitions of sizes might reduce the scatter of mass-size relation \citep[e.g.,][]{Miller2019,Trujillo2020} and further benefit the definition of UPGs.

% Find literature for quenched fraction as a function of distance to host (Einasto 1974, Spekkens2014, Karunakaran2022 for MW and M31).

% SAGA misses a fraction of red faint galaxies in their initial detection catalogs. This also explains the low quenched fraction of SAGA \citep{CarlstenELVES2022}.
% SAGA SB limit is 25. ARTEMIS is able to reproduce SAGA quenched fraction.

% \jiaxuan{UPG help us define mass-size lognormal, more diverse environment. distances.}

\subsection{UDG and UPG formation}
In this paper, one surprising finding is that although UPGs have extremely large size for their stellar mass, they have similar quiescent fraction as normal satellites in MW analogs. In ELVES, Greene et al. (in prep) also find no trend of quenched fraction on size. \citet{ELVES-I} find that the mass-size relation of satellites in MW analogs does not depend on the morphology (equivalently color) of satellites, suggesting that the quenching and morphological transformation involves very mild size evolution. Perhaps quenching and size growth happen separately. Then the question is what physics is responsible for the two processes respectively. In this section, we first review the quenching of MW satellites and the mechanisms for puffing up normal dwarfs to produce UDGs (UPGs). Then we combine the results presented in Section \ref{sec:results} and discuss possible implications on the formation and quenching of UDGs and UPGs. 
\jiaxuan{Cite the Pan et al. paper}

%%%%%%%%%%%%%%%%%%%
Isolated dwarf galaxies in the field are known to be star-forming \citep{Geha2012}, but satellites in the Local Group and Local Volume are more quiescent \citep{Grcevich2009,Spekkens2014,Wetzel2015,Putman2021,Baxter2021,CarlstenELVES2022,Karunakaran2022}. This difference hints that the MW environments play an important role in regulating the star formation activities in dwarf galaxies. There have been extensive works using simulations to study the quenching of satellites in MW analogs \citep[e.g.,][]{Simpson2018,Buck2019,Garrison-Kimmel2019,Simons2020,Joshi2021,Akins2021,Karunakaran2021,Font2022,Samuel2022}, and many of them are able to reproduce the observed quenched fraction in the Local Group and in the Local Volume.

@@

\section{Summary}\label{sec:summary}
\begin{itemize}
    \item we advocate studies for the quenched fraction as a function of size in simulations
